FEM Model Analysis

### 2021-09-10 FEM_R/model_analysis_core.Rmd
Added logic for the confidence intervals on the AgeUK figures into the model_analysis_core.Rmd script

```{r echo = FALSE}
#AgeUK
male_au <- read.csv('../../../Validation/AgeUK-chronDisease-MALE.csv')
female_au <- read.csv('../../../Validation/AgeUK-chronDisease-FEMALE.csv')

# FEM 2014 detailed output
#FEM_2014 <- read_dta('ELSA_Baseline/detailed_output/y2014_rep1.dta')
## extract males and females
#mFEM_2014 <- FEM_2014 %>% filter(male == 1)
#fFEM_2014 <- FEM_2014 %>% filter(male == 0)

# FEM 2014 summary
#FEM <- read_dta('ELSA_Baseline/ELSA_Baseline_summary.dta')
FEM <- read_dta('ELSA_AgeUK_core_valid/ELSA_AgeUK_core_valid_summary.dta')

@@

# Convert value from fraction to percentage
pivoted.FEM$value <- pivoted.FEM$value * 100

# Rename cols to enable reshaping
male_au <- male_au %>%
                dplyr::rename(m_6064 = X60.64, m_6569 = X65.69, m_7074 = X70.74,
                       m_7579 = X75.79, m_8084 = X80.84, m_8589 = X85.89,
                       m_9094 = X90.94, m_9599 = X95.99, m_100p = Over.100) %>%
                select(!Total)

female_au <- female_au %>%
                dplyr::rename(f_6064 = X60.64, f_6569 = X65.69, f_7074 = X70.74,
                       f_7579 = X75.79, f_8084 = X80.84, f_8589 = X85.89,
                       f_9094 = X90.94, f_9599 = X95.99, f_100p = Over.100) %>%
                select(!Total)

# Now need to reshape these datasets to long format
pivoted.male <- pivot_longer(data = male_au,
                             cols = m_6064:m_100p,
                             names_to = c('Gender', 'Age_Group'),
                             names_sep = '_')

pivoted.female <- pivot_longer(data = female_au,
                             cols = f_6064:f_100p,
                             names_to = c('Gender', 'Age_Group'),
                             names_sep = '_')

@@

# Now need to deal with the fact that ageUK data splits heart issues into 3 different conditions
# extract all heart related conditions for combining
#ageUK_heart <- filter(ageUK, Condition == c('Coronary Heart Disease', 'Heart Failure', 'Atrial Fibrillation'))
# Aggregate the values by gender and age group
#ageUK_heart <- aggregate(ageUK_heart$value, by = list(ageUK_heart$Gender, ageUK_heart$Age_Group), FUN = sum)
# Rename columns and add condition column back
#colnames(ageUK_heart) <- c('Gender', 'Age_Group', 'value')
#ageUK_heart$Condition <- 'Heart Problems'

# Now drop the heart problems from original ageUK and replace with aggregate
ageUK <- filter(ageUK, Condition != 'Coronary Heart Disease', Condition != 'Heart Failure', Condition != 'Atrial Fibrillation')
#ageUK <- rbind(ageUK, ageUK_heart)

# Rename a few just for completeness
#ageUK$Condition <- gsub("Cancer, recent", "Cancer", ageUK$Condition)
#ageUK$Condition <- gsub("COPD", "Lung Disease (COPD)", ageUK$Condition)

@@

#force Make to run this again

# Add column to specify this is FEM data
newFEM$source <- "FEM"

@@

# Function to filter the combined dataset and visualise
visAgeUKValid <- function(data, cd, gender, path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/validation/ageUK/') {

  if(gender == 'm') {
    full_gender <- 'Male'
  }
  else if(gender == 'f') {
    full_gender <- 'Female'
  }

@@

  # now plot!
  p <- ggplot(data = data, aes(x = Age_Group, y = value)) +
          geom_bar(aes(fill = source), stat = "identity", position = "dodge") +
          labs(title = paste(cd, full_gender, sep = ' '), x = 'Age Group', y = 'Proportion')

  # Save plot into in E-FEM_Paper/figures/
  ggsave(filename = paste0(cd, '_', gender, '.png'),
         plot = p,
         path = path,
         width = 6,
         height = 4)

@@

```{r}
FEM_base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')

>>>>

```{r echo = FALSE}
#AgeUK
male_au <- read.csv('../Validation/AgeUK-chronDisease-MALE_CI.csv')
female_au <- read.csv('../Validation/AgeUK-chronDisease-FEMALE_CI.csv')

# FEM 2014 summary
FEM <- read_dta('output/COMPLETE/ELSA_AgeUK_core_valid/ELSA_AgeUK_core_valid_summary.dta')

@@

# Convert value from fraction to percentage
pivoted.FEM$value <- pivoted.FEM$value * 100
# Set gender codes to upper case
pivoted.FEM$Gender <- toupper(pivoted.FEM$Gender)

# Rename variables for the pivot
male_au <- male_au %>%
                dplyr::rename(M_6064_total = M_60.64_total, M_6064_lower = M_60.64_l, M_6064_upper = M_60.64_u, 
                              M_6569_total = M_65.69_total, M_6569_lower = M_65.69_l, M_6569_upper = M_65.69_u,
                              M_7074_total = M_70.74_total, M_7074_lower = M_70.74_l, M_7074_upper = M_70.74_u,
                              M_7579_total = M_75.79_total, M_7579_lower = M_75.79_l, M_7579_upper = M_75.79_u,
                              M_8084_total = M_80.84_total, M_8084_lower = M_80.84_l, M_8084_upper = M_80.84_u,
                              M_8589_total = M_85.89_total, M_8589_lower = M_85.89_l, M_8589_upper = M_85.89_u,
                              M_9094_total = M_90.94_total, M_9094_lower = M_90.94_l, M_9094_upper = M_90.94_u,
                              M_9599_total = M_95.99_total, M_9599_lower = M_95.99_l, M_9599_upper = M_95.99_u,
                              M_100p_total = M_Over.100_total, M_100p_lower = M_Over.100_l, M_100p_upper = M_Over.100_u) %>%
                select(-M_Total_total, -M_Total_l, -M_Total_u)

female_au <- female_au %>%
                dplyr::rename(F_6064_total = F_60.64_total, F_6064_lower = F_60.64_l, F_6064_upper = F_60.64_u, 
                              F_6569_total = F_65.69_total, F_6569_lower = F_65.69_l, F_6569_upper = F_65.69_u,
                              F_7074_total = F_70.74_total, F_7074_lower = F_70.74_l, F_7074_upper = F_70.74_u,
                              F_7579_total = F_75.79_total, F_7579_lower = F_75.79_l, F_7579_upper = F_75.79_u,
                              F_8084_total = F_80.84_total, F_8084_lower = F_80.84_l, F_8084_upper = F_80.84_u,
                              F_8589_total = F_85.89_total, F_8589_lower = F_85.89_l, F_8589_upper = F_85.89_u,
                              F_9094_total = F_90.94_total, F_9094_lower = F_90.94_l, F_9094_upper = F_90.94_u,
                              F_9599_total = F_95.99_total, F_9599_lower = F_95.99_l, F_9599_upper = F_95.99_u,
                              F_100p_total = F_Over.100_total, F_100p_lower = F_Over.100_l, F_100p_upper = F_Over.100_u) %>%
                select(-F_Total_total, -F_Total_l, -F_Total_u)

# Now need to reshape these datasets to long format
pivoted.male <- pivot_longer(data = male_au,
                             cols = M_6064_total:M_100p_upper,
                             names_to = c('Gender', 'Age_Group', 'Type'),
                             names_sep = '_')

pivoted.female <- pivot_longer(data = female_au,
                             cols = F_6064_total:F_100p_upper,
                             names_to = c('Gender', 'Age_Group', 'Type'),
                             names_sep = '_')

# Now bring the confidence intervals back into columns because ggplot needs that format
# to plot them. Seems pretty daft to be honest but thats what we've got
pivoted.male <- pivot_wider(pivoted.male,
                            names_from = Type,
                            values_from = value)
pivoted.female <- pivot_wider(pivoted.female,
                            names_from = Type,
                            values_from = value)

@@

# Now drop the heart problems from original ageUK and replace with aggregate
ageUK <- filter(ageUK, Condition != 'Coronary Heart Disease', Condition != 'Heart Failure', Condition != 'Atrial Fibrillation')

@@

# Add column to specify this is FEM data
newFEM$source <- "FEM"
newFEM$total <- newFEM$value
newFEM <- select(newFEM, -value)

# Add column to specify this is FEM data
newFEM$source <- "FEM"
# Add column to specify these are all totals (no confidence intervals)
newFEM$lower <- NA
newFEM$upper <- NA

@@

# Function to filter the combined dataset and visualise
visAgeUKValid <- function(data, cd, gender, path = '/home/luke/Documents/E_FEM_clean/Deliverables/E-FEM_Paper/figures/validation/ageUK') {

  if(gender == 'M') {
    full_gender <- 'Male'
  }
  else if(gender == 'F') {
    full_gender <- 'Female'
  }

@@

  # now plot!
  p <- ggplot(data = data, aes(x = Age_Group, y = total)) +
          geom_bar(aes(fill = source), stat = "identity", position = position_dodge2()) +
          geom_errorbar(aes(ymin = lower, ymax = upper), position = position_dodge2(width = 1, padding = 0.5)) +
          labs(title = paste(cd, full_gender, sep = ' '), x = 'Age Group', y = 'Proportion')

  # Save plot into in E-FEM_Paper/figures/
  #ggsave(filename = paste0(cd, '_', gender, '.png'),
  #      plot = p,
  #      path = path,
  #      width = 7,
  #      height = 5)

@@

```{r echo=False}
FEM_base <- read_dta('ELSA_core_base/ELSA_core_base_summary.dta')
